Assignment: Referee Report

### 2024-10-08 assignments/research_proposal/peer_review.Rmd
lecture 11

- Clarity of the writing (grammar, organization, and structure),
- Minor inconsistencies in the theoretical argument,
- Specific technical clarifications needed in the research design or data analysis,
- Suggestions for additional literature that could strengthen the theoretical framework,
- Formatting issues or citation inaccuracies.
- For each minor point, include:

>>>>

- Clarity of the writing (grammar, organization, and structure)
- Minor inconsistencies in the theoretical argument
- Specific technical clarifications needed in the research design or data analysis
- Suggestions for additional literature that could strengthen the theoretical framework
- Formatting issues or citation inaccuracies

### 2024-10-08 assignments/research_proposal/peer_review.tex
lecture 11

\begin{itemize}
\tightlist
\item
  Clarity of the writing (grammar, organization, and structure),
\item
  Minor inconsistencies in the theoretical argument,
\item
  Specific technical clarifications needed in the research design or data analysis,
\item
  Suggestions for additional literature that could strengthen the theoretical framework,
\item
  Formatting issues or citation inaccuracies.
\item
  For each minor point, include:
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  Clarity of the writing (grammar, organization, and structure)
\item
  Minor inconsistencies in the theoretical argument
\item
  Specific technical clarifications needed in the research design or data analysis
\item
  Suggestions for additional literature that could strengthen the theoretical framework
\item
  Formatting issues or citation inaccuracies
\end{itemize}
